### 2017-04-02 paper.tex
Add language on sync bytes

Designing and building a communication layer that can be relied up was an
important requirement for the rest of the project. Transmitting as much as
possible of a mission's scientific data is primordial in case the platform
is carried too far by winds and cannot be recovered after landing.

@@

\begin{figure}[H]
    \begin{bytefield}{24}
        \bitheader{0,7,8,15,16,23} \\
        \bitbox{8}{version} & \bitbox{16}{sequence number} \\
            \wordbox[lrt]{1}{payload data} \\
            \skippedwords \\
            \wordbox[lrb]{1}{}
    \end{bytefield}
    \centering
    \caption{Original AHABus Frame Format}
    \label{fig:frame-fmt-orig}
\end{figure}

@@

\newpage
\printbibliography[heading=bibnumbered]

>>>>

Designing and building a communication protocol that can be relied up was an
important requirement for the rest of the project. Transmitting as much as
possible of a mission's scientific data is primordial in case the platform
is carried too far by winds and cannot be recovered after landing.

@@

\begin{figure}[H]
    \begin{center}
    \begin{bytefield}[bitwidth=0.65em]{64}
        \bitheader{0,8,24,40} \\
        \bitbox{8}{version} &
        \bitbox{16}{sequence number} &
        \bitbox{40}{data}
    \end{bytefield}
    \end{center}
    \centering
    \caption{AHABus Frame Format – Second Iteration}
    \label{fig:frame-fmt-orig}
\end{figure}

This preliminary design proved impossible to work with. While it encapsulates
the required data and metadata, it does not provide any way to identify the
start or the end of a frame in a raw binary stream, which would have rendered
parsing an incoming frame stream impossible.

To solve this issue, a ``start sequence'' was added at the very beginning of
the frame. When parsing frames from a binary stream, the decoder must ignore
bytes until the start sequence (a single byte of value \texttt{0xAA} followed
by a single byte of value \texttt{0x5A}) occurs. Once the frame sequence is
detected, the frame's end is detected once 256 bytes have been received.

\begin{figure}[H]
    \begin{center}
    \begin{bytefield}[bitwidth=0.65em]{64}
        \bitheader{0,8,16,24,40} \\
        \bitbox{8}{0xAA} & \bitbox{8}{0x5A} & \bitbox{8}{version} &
        \bitbox{16}{sequence number} &
        \bitbox{24}{data}
    \end{bytefield}
    \end{center}
    \centering
    \caption{AHABus Frame Format – Second Iteration}
    \label{fig:frame-fmt-2}
\end{figure}

% Go to the magic website http://madebyevan.com/fsm/
\begin{figure}[H]
    \begin{center}
    \begin{tikzpicture}[scale=0.2]
    \tikzstyle{every node}+=[inner sep=0pt]
    \draw [black] (23.9,-13.4) circle (3);
    \draw (23.9,-13.4) node {$Wait$};
    \draw [black] (53.5,-13.4) circle (3);
    \draw (53.5,-13.4) node {$Sync$};
    \draw [black] (38.6,-30.7) circle (3);
    \draw (38.6,-30.7) node {$Frame$};
    \draw [black] (26.719,-12.375) arc (107.79277:72.20723:39.209);
    \fill [black] (50.68,-12.37) -- (50.07,-11.65) -- (49.77,-12.61);
    \draw (38.7,-10) node [above] {$byte=AA$};
    \draw [black] (53.11,-16.371) arc (-12.09889:-69.37588:18.591);
    \fill [black] (41.48,-29.87) -- (42.41,-30.06) -- (42.05,-29.12);
    \draw (49.56,-26.05) node [right] {$byte=5A$};
    \draw [black] (35.918,-29.359) arc (-119.94439:-159.34576:25.489);
    \fill [black] (24.79,-16.26) -- (24.61,-17.19) -- (25.54,-16.84);
    \draw (28.67,-25.22) node [left] {$read=256$};
    \draw [black] (51.972,-15.968) arc (-3.02212:-291.02212:2.25);
    \draw (47.22,-18.39) node [left] {$byte=AA$};
    \fill [black] (50.53,-13.75) -- (49.76,-13.21) -- (49.71,-14.21);
    \draw [black] (25.724,-11.023) arc (137.60109:42.39891:17.571);
    \fill [black] (25.72,-11.02) -- (26.63,-10.77) -- (25.89,-10.1);
    \draw (38.7,-4.8) node [above] {$byte!=AA$};
    \end{tikzpicture}
    \end{center}
    \centering
    \caption{AHABus Frame Synchronisation}
\end{figure}

@@

\newpage
\printbibliography[heading=bibnumbered, title=References]
